### 2023-09-04 proofs/tex/alg-pos-subtyping-lemmas.tex
Grammar update: Γ = set

        Since $[[â⁺[Δ] ∊ Θ]]$ and $[[Δ ⊢ iQ']]$, 
        it is clear that $[[ Θ ⊢ (â⁺ :≥ iQ') : â⁺]]$.

@@

            By inversion, $[[Γ ; dom(Θ) ⊢  ∃nbs.α̂⁺]]$ implies $[[â⁺[Δ] ∊ Θ]]$ for some 
            $[[{Δ} ⊆ {Γ}]]$.

            By \cref{lemma:quant-rule-decomposition} applied twice, 
            $[[ Γ ⊢ ∃nbs.[uσ]α̂⁺ ≥ ∃ncs.iQ0 ]]$ implies
            $[[ Γ,ncs  ⊢ [iNs/nbs][uσ]α̂⁺ ≥ iQ0 ]]$ for some $[[iN]]$, 
            and since $[[ {nbs} ∩ fv([uσ]α̂⁺) ⊆ {nbs} ∩ {Θ(α̂⁺)} ⊆ {nbs} ∩ {Γ} = ∅ ]]$,
            $[[ [iNs/nbs][uσ]α̂⁺ = [uσ]α̂⁺ ]]$, that is $[[ Γ,ncs ⊢ [uσ]α̂⁺ ≥ iQ0]]$.

@@

            Why does the upgrade procedure terminate?
            Because $[[ [uσ]α̂⁺ ]]$ satisfies the pre-conditions of the completeness of the upgrade
            (\cref{lemma:upgrade-completeness}):
            \begin{enumerate}
                \item $[[Δ ⊢ [uσ]α̂⁺ ]]$ because $[[Θ ⊢ uσ : α̂⁺]]$ and $[[α̂⁺[Δ] ∊ Θ]]$,
                \item $[[ Γ,ncs ⊢ [uσ]α̂⁺ ≥ iQ0]]$ as noted above
            \end{enumerate}

@@

            By inversion, $[[ Γ ⊢ [σ][uσ]uP' ≥ iQ' ]]$ for some $[[Γ, nbs ⊢ σ : nas]]$.
            Since $[[σ]]$ and $[[uσ]]$ have disjoint domains,
            and the range of one does not intersect with the domain of the other,
            they commute, i.e. $[[ Γ, nbs ⊢ [uσ][σ]uP' ≥ iQ' ]]$
            (notice that the tree inferring this judgement is 
            a proper subtree of the tree inferring 
            $[[ Γ ⊢ [uσ]uP ≥ iQ ]]$).

@@

            Let us construct such a substitution $[[us0]]$:
                \[
                    [[ [uσ0]β̂± ]]  = 
                    \begin{cases}
                    [[ [σ]αi⁻ ]] & \text{if } [[β̂±]] = [[αî⁻]] \in [[{â⁻*} ∩ uv(uP0)]] \\
                    [[ [uσ]β̂± ]] & \text{if } [[β̂±]] \in [[ uv(uP') ]]
                    \end{cases}
            \]
            It is easy to see $[[Θ, â⁻*[Γ, nbs] ⊢ uσ0 : uv(uP0)]]$:
            $[[uv(uP0)]] = [[ uv([â⁻*/nas]uP') ]] = [[{â⁻*} ∩ uv(uP0) ∪ uv(uP')]]$. Then
            \begin{enumerate}
                    \item for $[[αî⁻]] \in [[{â⁻*} ∩ uv(uP0)]]$, $[[ (Θ, â⁻*[Γ, nbs])(αî⁻) ⊢ [uσ0] αî⁻]]$, 
                    i.e. $[[ Γ, nbs ⊢ [σ]αi⁻ ]]$ holds since $[[Γ, nbs ⊢ σ : nas]]$,
                    \item for $[[β̂±]] \in [[ uv(uP') ]] \subseteq [[dom(Θ)]]$, $[[ (Θ, â⁻*[Γ, nbs])(β̂±) ⊢ [uσ0] β̂± ]]$,
                    i.e. $[[Θ(β̂±) ⊢ [uσ] β̂± ]]$ holds since $[[Θ ⊢ uσ : uv(uP)]]$ and $[[β̂±]] \in [[ uv(uP') ]] = [[uv(uP)]]$.
            \end{enumerate}

>>>>

        Since $[[â⁺[Δ] ∊ Θ]]$ and $[[Δ ⊢ iQ']]$, 
        it is clear that $[[ Θ ⊢ (â⁺ :≥ iQ') : {â⁺}]]$.

@@

            By inversion, $[[Γ ; dom(Θ) ⊢  ∃nbs.α̂⁺]]$ implies $[[â⁺[Δ] ∊ Θ]]$ for some 
            $[[{Δ} ⊆ Γ]]$.

            By \cref{lemma:quant-rule-decomposition} applied twice, 
            $[[ Γ ⊢ ∃nbs.[uσ]α̂⁺ ≥ ∃ncs.iQ0 ]]$ implies
            $[[ Γ,ncs  ⊢ [iNs/nbs][uσ]α̂⁺ ≥ iQ0 ]]$ for some $[[iN]]$, 
            and since $[[ {nbs} ∩ fv([uσ]α̂⁺) ⊆ {nbs} ∩ {Θ(α̂⁺)} ⊆ {nbs} ∩ Γ = ∅ ]]$,
            $[[ [iNs/nbs][uσ]α̂⁺ = [uσ]α̂⁺ ]]$, that is $[[ Γ,ncs ⊢ [uσ]α̂⁺ ≥ iQ0]]$.

@@

            Why does the upgrade procedure terminate?
            Because $[[ [uσ]α̂⁺ ]]$ satisfies the pre-conditions of the completeness of the upgrade
            (\cref{lemma:upgrade-completeness}):
            \begin{enumerate}
                \item $[[Δ ⊢ [uσ]α̂⁺ ]]$ because $[[Θ ⊢ uσ : {α̂⁺}]]$ and $[[α̂⁺[Δ] ∊ Θ]]$,
                \item $[[ Γ,ncs ⊢ [uσ]α̂⁺ ≥ iQ0]]$ as noted above
            \end{enumerate}

@@

            By inversion, $[[ Γ ⊢ [σ][uσ]uP' ≥ iQ' ]]$ for some $[[Γ, nbs ⊢ σ :{nas}]]$.
            Since $[[σ]]$ and $[[uσ]]$ have disjoint domains,
            and the range of one does not intersect with the domain of the other,
            they commute, i.e. $[[ Γ, nbs ⊢ [uσ][σ]uP' ≥ iQ' ]]$
            (notice that the tree inferring this judgement is 
            a proper subtree of the tree inferring 
            $[[ Γ ⊢ [uσ]uP ≥ iQ ]]$).

@@

            Let us construct such a substitution $[[us0]]$:
                \[
                    [[ [uσ0]β̂± ]]  = 
                    \begin{cases}
                    [[ [σ]αi⁻ ]] & \text{if } [[β̂±]] = [[αî⁻]] \in [[{â⁻*} ∩ uv(uP0)]] \\
                    [[ [uσ]β̂± ]] & \text{if } [[β̂±]] \in [[ uv(uP') ]]
                    \end{cases}
            \]
            It is easy to see $[[Θ, â⁻*[Γ, nbs] ⊢ uσ0 : uv(uP0)]]$:
            $[[uv(uP0)]] = [[ uv([â⁻*/nas]uP') ]] = [[{â⁻*} ∩ uv(uP0) ∪ uv(uP')]]$. Then
            \begin{enumerate}
                    \item for $[[αî⁻]] \in [[{â⁻*} ∩ uv(uP0)]]$, $[[ (Θ, â⁻*[Γ, nbs])(αî⁻) ⊢ [uσ0] αî⁻]]$, 
                    i.e. $[[ Γ, nbs ⊢ [σ]αi⁻ ]]$ holds since $[[Γ, nbs ⊢ σ :{nas}]]$,
                    \item for $[[β̂±]] \in [[ uv(uP') ]] \subseteq [[dom(Θ)]]$, $[[ (Θ, â⁻*[Γ, nbs])(β̂±) ⊢ [uσ0] β̂± ]]$,
                    i.e. $[[Θ(β̂±) ⊢ [uσ] β̂± ]]$ holds since $[[Θ ⊢ uσ : uv(uP)]]$ and $[[β̂±]] \in [[ uv(uP') ]] = [[uv(uP)]]$.
            \end{enumerate}

### 2023-09-04 proofs/tex/anti-unification-lemmas.tex
Grammar update: Γ = set

        \item \ruleref{\ottdruleAUAULabel}, which applies 
        when other rules do not, and $[[G ⊢ iNi]]$,
        returning as the result $[[(Ξ, uM, aus1, aus2)]] = $
        $[[(â⁻_{iN1, iN2}, â⁻_{iN1, iN2}, (â⁻_{iN1, iN2} :≈ iN1) ,  (â⁻_{iN1, iN2} :≈ iN2))]]$.

        \begin{enumerate}
            \item $[[Γ ; Ξ ⊢ uM]]$ is rewritten as $[[Γ ; â⁻_{iN1, iN2} ⊢ â⁻_{iN1, iN2}]]$,
                which holds trivially;
            \item $[[Γ ; · ⊢ ausi : Ξ]]$ is rewritten as $[[Γ ; · ⊢ (â⁻_{iN1, iN2} :≈ iNi) : â⁻_{iN1, iN2}]]$,
                which holds since $[[Γ ⊢ iNi]]$ by the premise of the rule;
            \item $[[ [ausi] uM = iNi ]]$ is rewritten as $[[ [â⁻_{iN1, iN2} :≈ iNi] â⁻_{iN1, iN2} = iNi ]]$,
                which holds trivially by the definition of substitution.
        \end{enumerate}

>>>>

        \item \ruleref{\ottdruleAUAULabel}, which applies 
        when other rules do not, and $[[G ⊢ iNi]]$,
        returning as the result $[[(Ξ, uM, aus1, aus2)]] = $
        $[[({â⁻_{iN1, iN2}}, â⁻_{iN1, iN2}, (â⁻_{iN1, iN2} :≈ iN1) ,  (â⁻_{iN1, iN2} :≈ iN2))]]$.

        \begin{enumerate}
            \item $[[Γ ; Ξ ⊢ uM]]$ is rewritten as $[[Γ ; { â⁻_{iN1, iN2} } ⊢ â⁻_{iN1, iN2}]]$,
                which holds trivially;
            \item $[[Γ ; · ⊢ ausi : Ξ]]$ is rewritten as $[[Γ ; · ⊢ (â⁻_{iN1, iN2} :≈ iNi) : {â⁻_{iN1, iN2}}]]$,
                which holds since $[[Γ ⊢ iNi]]$ by the premise of the rule;
            \item $[[ [ausi] uM = iNi ]]$ is rewritten as $[[ [â⁻_{iN1, iN2} :≈ iNi] â⁻_{iN1, iN2} = iNi ]]$,
                which holds trivially by the definition of substitution.
        \end{enumerate}
